\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-21 icse/conclusion.tex
Till Sec. 6

We indiciate the problem that existing JavaScript semantics are not suitable for
annually updated cadence of ECMAScript specifications. We propose a tool \( \tool \),
JavaScript IR-based Semantics Extraction Toolchain to mechanize extracting syntax
and semantics from ECMAScript specifications. The most important modules are
the parser generator and the algorithm compiler. The parser generator generates
parsers from given \( \bnfes \) in lookahead parsers we proposed. the algorithm
compiler compiles given abstract algorithm written in structured natural language
into \( \ires \) functions. It is dependent on given compile rules and we provide
general compile rules for existing ECMAScript specifications. Moroever, we also
develop the rule assistant to diagnose root causes of not yet convertible algorithms.
It aids to modify compile rules for specification updates. We evaluate \( \tool \)
based on the next version of ECMAScript specification (2020) with the official conformance test
suite (test262). The extracted semantics passed all \inred{XXXXX} tests in test262
and we show that the tool is alo applicable into in-progress language features
by a case study. Moreover, we found \inred{four} real specification errors via \( \tool \)
and TC39 confirms all of them.

>>>>

We indiciate the problem that existing JavaScript semantics are not suitable for
annually updated cadence of ECMAScript specifications. We propose a tool \( \tool \),
JavaScript IR-based Semantics Extraction Toolchain to mechanize extracting syntax
and semantics from ECMAScript specifications. The most important modules are
the parser generator and the algorithm compiler. The parser generator generates
parsers from given \( \bnfes \) in lookahead parsers we proposed. the algorithm
compiler compiles given abstract algorithm written in structured natural language
into \( \ires \) functions. It is dependent on given compile rules and we provide
general compile rules for existing ECMAScript specifications. Moroever, we also
develop the rule assistant to diagnose root causes of not yet convertible algorithms.
It aids to modify compile rules for specification updates. We evaluate \( \tool \)
based on the next version of ECMAScript specification (2020) with the official conformance test
suite (Test262). The extracted semantics passed all \inred{XXXXX} tests in Test262
and we show that the tool is alo applicable into in-progress language features
by a case study. Moreover, we found three real specification errors via \( \tool \)
and TC39 confirms all of them.

### 2019-08-21 icse/eval.tex
Till Sec. 6

We evaluate \( \tool \) based on the following four research questions:
\begin{itemize}
  \item RQ2) \textbf{Effectiveness} Is \( \tool \) effective to extract syntax and
    semantics of existing ECMAScript specifications?
  \item RQ1) \textbf{Correctness} Does \( \tool \) correctly extract JavaScript syntax
    and semantics from ECMAScript 2020 speicification?
  \item RQ3) \textbf{Adaptability} Does \( \tool \) deal with future proposed features?
  \item RQ4) \textbf{Specification Error Detection} What specification errors
    are detected by \( \tool \)?
\end{itemize}

@@

\begin{figure}[t]
  \[
    \begin{array}{c|r|r|r|r|r?r}
      \hline
      \textbf{version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\hline
      \text{\# lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\\hline
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \hline
      \textbf{old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{new version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\hline
      \Delta \; \text{\# lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\\hline
    \end{array}
  \]
  \caption{The number of productions for lexical and
  syntactic grammars in ECMAScript specifications.}
  \label{fig:syntax-all-version}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.23\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem.png}
    \caption{Evaluation results for each version}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.20\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
    \caption{Evaluation results for each difference of adjacent versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{The result of the parser generator and the algorithm compiler for
  ECMAScript specifications.}
  \label{fig:all-version}
\end{figure}

We discuss the effectiveness of \( \tool \) by applying it into existing ECMAScript specifications.
The evaluation focuses on how many productions and abstract algorithms are covered by
our tool 1) in each version, and 2) in each difference between adjacent versions.
Figure~\ref{fig:all-version} shows the result of \( \tool \) from ECMAScript 2016
to 2020. While ECMAScript 5.1 is the first version that officially supports
the specification in HTML. However, two oldest versions ECMAScript 5.1 and 2015 are written
in quite different styles with recent versions including HTML tags used in abstract algorithms.
Thus, we evaluate only five recent versions from ECMAScript 2016 to 2020.

First, we evaluate that the \textsf{Parser Generator} in \( \tool \) successfully generate
parsers from all target versions of ECMAScript specifications. As described in
Figure~\ref{fig:syntax-all-version}, lexical and syntactic grammars
have \inred{XX} and \inred{XXX} productions in average, respectively.
Moreover, JavaScript syntax are annually updated of \inred{X} productions for lexical grammars
and \inred{XX} productions for syntactic grammars in average.

Figure~\ref{fig:all-version} shows the evaluation results for semantics.
The \textsf{Algorithm Compiler} with the compile rules described in Section~\ref{sec:impl}
has \inred{XX\%} success rates for existing specifications in average. Moreover,
\( \tool \) are also effective to update existing semantics
because \inred{XX\%} of changed or newly defined algorithms are automatically
compiled into \( \ires \) functions. Thus, we believe that \( \tool \) effectively
reduce the effort to extract syntax and semantics of JavaScript
not only when developing them from the scratch, but also updating existing syntax and semantics.

\subsection{Correctness}

\begin{table}
  \centering
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Negative tests & 2,628\\\hdashline
    Non-strict tests & 1,064\\\hdashline
    Module tests& 642 \\\hdashline
    Inessential built-in objects tests & \inred{XXXX}\\\hdashline
    Tests for not yet modeled semantics & \inred{XXXX} \\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
  \caption{The results of tests in the test262 for ECMAScript 2020.}
  \label{table:test262}
\end{table}

To evaluate that \( \tool \) correctly extracts semantics, we develop the JavaScript
interpreter based on the extracted syntax and semantics from ECMAScript 2020.
Among \inred{XXXX} algorithms in ECMAScript 2020, \inred{XXX} algorithms
are related to the not-supported language features. And \inred{XXXX} algorithms
are automatically compiled into \( \ires \) functions via the \textsf{Algorithm Compiler}.
Among remaining \inred{XXX} algorithms, we select \inred{XX} algorithms
essential parts of overall semantics and manually implement corresponding \( \ires \)
functions. As described in Section~\ref{sec:impl}, we also
carefully implement \textsf{Global Setting}.

We test our JavaScript interpreter based on test262, the conformance test suite
that is officially provided by the committee TC39. However, the current version of
test262 also provides tests for other extensions or in-progress features.
Thus, we exclude them to focus on only the semantics of ECMAScript 2020.
Figure~\ref{table:test262} describes how to break down tests and the test results of extracted
semantics. We use test262 written in \inred{August 6, 2019}. In that version,
test262 consists of 36,794 tests and we first exclude \inred{XXXX} tests
for extensions and in-progres features. We also remove \inred{XXXX} tests for
not-supported features; non-strict codes, intricate built-in objects, and modules.
Finally, we tested \inred{XXXXX} applicable tests with our JavaScript interpreter.
Among them, \inred{XXXXX} tests are successfully passed and all other tests are
not passed just because of not yet modeled abstract algorithms. It means that
all semantics extracted from \( \tool \) are perfectly correct.

% TODO if some tests are failed, categorize them and explain why they are failed.

\subsection{Adaptability}

We also check that \( \tool \) deals with future language features for adaptability.
ECMAScript specifications are managed as open-sources and proposals of in-progress language
features by following the TC39 process. Such proposals are tracked in the separated repository~\cite{proposals}
and thare are six different stages for them; Stage from 0 to 3, and finished or inactive proposals.
Each proposal starts with Stage 0 and is promoted into Stage 3 through Stage 1 and 2.
The committee (TC39) regularly examins the Stage 3 proposals to decide their next stages.
If the proposals are confirmed, the committee changes their stages into finished
and integrate them into the next version of ECMAScript specification.
Otherwise, the committee changes them into inactive. Our tool \( \tool \) is also applicable
into not yet finished proposals and we advance a case study for a Stage 3 proposal.

The optional chain syntax (\( \code{?.} \)) is one of Stage 3 proposals that removes the
boilerplate codes; \( \code{x \&\& x.p} \). The code first checks that the value of
the variable \( \code{x} \) is not \( \code{undefined} \) and then access its
property \( \code{p} \). With the optional chain syntax, we could redece the code size
by implementing as \( \code{x?.p} \). We apply this proposal into ECMAScript 2020 specification
and evaluate \( \tool \) to extract the semantics from the extended specification.
For the extended speicification, the \textsf{Parser Generator} successfully handle
three updated lexical productions and three updated syntactic productions.
For semantics, there 22 updated abstract algorithms. At the first attempt,
the \textsf{Algorithm Compiler} suceedes to compile only 10 algorithms.
However, we notice that several algorithm steps have diffrent styles with
the existing ECMAScript specifications. Thus, we revise them into the original
writing styles and report the revision into the GitHub repository of the proposal.
The authors of this proposal approved and accepted our pull requests.
After revisions, 21 of 22 algorithms are successfully compiled and we manually
compile only one algorithm. In the test262, there are 33 tests related to the optional chain
syntax and six tests of them are semantics tests. The semantics extracted with
the optional chain proposal successfully pass all the six semantics tests.
This case study shows the adaptability of \( \tool \) for future language features
and also \( \tool \) might be possible to be used as a specification writing guidance.

\subsection{Specification Error Detection}

We found three specification errors in ECMAScript 2020 via \( \tool \).
We fixed them and sent pull requests into the official GitHub repository of
ECMAScript specification~\cite{es2020}. They were all confirmed by TC39
and will be fixed in the next release.

First, we found that \textbf{VarScopedDeclarations} syntax-directed algorithms of
specific cases of \textit{IterationStatement} are ambigious.
The \textbf{VarScopedDeclarations} algorithm is used to initially define
the variable declarations before entering speicific scopes.
However, the following iteration syntax has two different
\textbf{VarScopedDeclarations} algorithms:
\[
  \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
\textit{AssignmentExpression} \; \code{)} \; \textit{Statement}
\]
The \textsf{Spec Extractor} of \( \tool \) detects its duplicated
semantics during automatically extracting abstract algorithms into JSON files.

For the \textbf{ExpectedArgumentCount} algorithm, we found that
there are missing cases for some syntax. This algorithm counts the number of
expected arugments of a specific parameters. However, it does not cover all
the cases. For example, if there exists only one formal parameter,
the ECMAScript 2020 specification does not provide any semantics.
We detect this error during evaluations of test262 tests under
the extracted semantics via \( \tool \). It throws an error that there
is no \textbf{ExpectedArgumentCount} algorithm for specific tests.

Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to
specify ECMAScript and beautify a raw speicification HTML file
into a more visible HTML file. At the first time, we though that
we found a missing case for the \textbf{IsFunctionDefinition}
algorithm of unnamed function expressions. However, in the
raw specification HTML file, there are no missing cases. We investigate
why it happens and realize that \textsf{Ecmarkup} itself has
a bug to silently remove the {\small opt} subscript in \( \code{collapsed} \)
syntax mode. It is already discovered bug but our tool found this bug
in a mechanical way.

>>>>

We evaluate \( \tool \) based on the following four research questions:
\begin{itemize}[leftmargin=0.5cm]
\item RQ1. \textbf{Effectiveness:} Does \( \tool \) effectively reduce
manual efforts in extracting the syntax and semantics from existing
ECMAScript specifications? 
\item RQ2. \textbf{Correctness:} Do the extracted syntax and semantics
from ECMAScript 2020 behave correctly?
\item RQ3. \textbf{Adaptability:} Is \( \tool \) applicable to
incomplete feature proposals?
\item RQ4. \textbf{Usefulness:} Does \( \tool \) detect any
specification errors?
\end{itemize}

@@

\begin{figure}[t]
  \[
    \begin{array}{c?r|r|r|r|r?r}
      \textbf{Version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \multicolumn{1}{c}{\textbf{avg.}}\\\toprule
      \text{\# Lexical prod.}
      & \text{78}
      & \text{78}
      & \text{78}
      & \text{81}
      & \text{81}
      & \text{79.2}\\\hline
      \text{\# Syntactic prod.}
      & \text{157}
      & \text{167}
      & \text{167}
      & \text{174}
      & \text{175}
      & \text{168}\\
    \end{array}
  \]
  \[
    \begin{array}{c|r|r|r|r?r}
      \textbf{Old version}
      & \multicolumn{1}{c|}{\textbf{2016}}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c?}{\textbf{2019}}
      & \multirow{2}{*}{\textbf{avg.}}\\\cline{1-5}
      \textbf{New version}
      & \multicolumn{1}{c|}{\textbf{2017}}
      & \multicolumn{1}{c|}{\textbf{2018}}
      & \multicolumn{1}{c|}{\textbf{2019}}
      & \multicolumn{1}{c?}{\textbf{2020}}
      & \\\toprule
      \Delta \; \text{\# Lexical prod.}
      & \text{3}
      & \text{5}
      & \text{6}
      & \text{0}
      & \text{4.7}\\\hline
      \Delta \; \text{\# Syntactic prod.}
      & \text{140}
      & \text{15}
      & \text{8}
      & \text{2}
      & \text{55}\\
    \end{array}
  \]
  \caption{Number of productions in specifications,
from \textit{all} of which \( \tool \) automatically generated parsers}
  \label{fig:syntax-all-version}
\end{figure}

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.23\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem.png}
    \caption{Results for different versions}
    \label{fig:semantics-all-version}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.20\textwidth}
    \includegraphics[width=\textwidth]{img/all-version-sem-delta.png}
    \caption{Results for differences between versions}
    \label{fig:semantics-all-version-delta}
  \end{subfigure}
  \caption{Number of abstract algorithms in specifications, from which
\( \tool \) generated the JavaScript semantics}
  \label{fig:all-version}
\end{figure}

We evaluate the effectiveness of \( \tool \) by applying it to the
most recent five versions of the ECMAScript specifications, ECMAScript
2016 to 2020.  We measured for how many grammar productions and
abstract algorithms \( \tool \) automatically generates parsers and
semantics, respectively, in two respects: 1) in each version and 2) in
each difference between adjacent versions.

For syntax, we measured the number of grammar productions for which
\textsf{Parser Generator} automatically generated parsers.  As summarized in
Figure~\ref{fig:syntax-all-version}, the average numbers of lexical and
syntactic grammar productions are \inred{XX} and \inred{XXX}, respectively.
In addition, the average numbers of annually updated lexical and
syntactic grammar productions between adjacent versions are \inred{X}
and \inred{XX}, respectively.  We report that \( \tool \)
automatically generated parsers for \textit{all} the productions.

For semantics, we measured the number of abstract algorithms that
\textsf{Algorithm Compiler} with the compile rules described in
Section~\ref{sec:impl} automatically covered.
Figure~\ref{fig:all-version} shows that \( \tool \) could
automatically extract semantics with the \inred{XX\%} success rate on
average for existing specifications, and \inred{XX\%} for changed or
newly defined algorithms.  Thus, we believe that \( \tool \) effectively
reduces the efforts to extract the syntax and semantics of JavaScript
not only for developing them from scratch, but also for updating
existing ones.

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,803\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,217}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,064\\\hdashline
    Module tests& 642 \\\hdashline
    Inessential built-in object tests & \inred{XXXX}\\\hdashline
    Non-standard negative tests & 2,628\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
\end{table}

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 1,601 algorithms in ECMAScript 2020,
\inred{XXX} algorithms are relevant to the excluded language features
discussed in Section~\ref{sec:exclusion}, and \inred{XXXX} algorithms
are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining \inred{XXX} algorithms, we selected \inred{XX}
algorithms that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions.

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of \inred{August 6, 2019}.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,577 tests for
extensions and in-progress features.  We also excluded \inred{XXXX}
tests for excluded features and non-standard negative tests.
Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
interpreter and they all successfully passed, which means that all the
semantics extracted from \( \tool \) are perfectly correct.

% TODO if some tests failed, categorize them and explain why they failed.

\subsection{Adaptability}
We show the adaptability of \( \tool \) with one case study: applying
it to an incomplete feature proposal.  Because ECMAScript is an open
standard language, various proposals are available with their own
specification changes and tests by following the TC39 process.  A
separate repository~\cite{proposals} maintains such proposals with six
different stages: Stage 0 to Stage 3, Finished, and Inactive.  Each
proposal starts with Stage 0, and the TC39 committee regularly
examines Stage 3 proposals to decide their next stages.  If a proposal
is confirmed, the committee changes its stage to Finished and
integrates it into the next version of the ECMAScript specification.
Otherwise, the committee changes its stage to Inactive.  Thus, we
applied \( \tool \) to one Stage 3 proposal.
%https://github.com/tc39/proposal-optional-chaining

The optional chaining operator (\( \code{?.} \)) is one of Stage 3
proposals that removes specific boilerplate code.  It detects a code
pattern like \( \code{x \&\& x.p} \), which first checks that the
value of \( \code{x} \) is not \( \code{undefined} \) and then
accesses its property \( \code{p} \).  With the optional chaining
operator, we can reduce code size by implementing it as \( \code{x?.p} \).
We extended ECMAScript 2020 with this proposal and applied \( \tool \)
to the extended specification.  We found that \textsf{Parser Generator}
successfully handled three updated lexical productions and three
updated syntactic productions.  For semantics, the proposal had 22
updated abstract algorithms.  At the first attempt,
\textsf{Algorithm Compiler} succeeded compiling only 10 algorithms.
However, we noticed that several algorithm steps have different styles
from existing ECMAScript specifications.  Thus, we revised them to the
original style, sent three pull requests to the GitHub repository
of the proposal, and the authors of the proposal accepted our pull
requests\footnote{The URL of three pull requests are anonymized 
due to a double-blind review process.}.  After revision, 21 of 22
algorithms are successfully compiled and we manually compiled only one
algorithm.  Test262 has 33 tests for the optional chaining operator
and six of them are semantics tests.  The semantics extracted with the
optional chaining operator proposal successfully passed all the six
semantics tests.  This case study shows that \( \tool \) is applicable
to future language features and it could be useful as a specification
writing guide.

\subsection{Usefulness}
We show the usefulness of \( \tool \) with one case study:
specification error detection.  While applying \( \tool \) to
ECMAScript 2020, we found three specification errors.  We fixed them
and sent pull requests to the official GitHub repository of
ECMAScript~\cite{es2020}.  They were all confirmed by TC39
and will be fixed in the next release \footnote{The URL of three pull
requests are anonymized due to a double-blind review process.}.

% https://github.com/tc39/ecma262/pull/1661
% https://github.com/tc39/ecma262/pull/1662
% https://github.com/tc39/ecma262/pull/1663
The first error we found is an ambiguous production for
\textit{IterationStatement}.  For some
specific cases, the syntax-directed algorithm for
\textbf{VarScopedDeclarations} is ambiguous.
Our \( \tool \) detected the duplicated semantics while automatically
extracting the abstract algorithms in JSON files.

The second error is that the \textbf{ExpectedArgumentCount} algorithm
has missing cases.  While this algorithm counts
the number of expected arguments of given formal parameters, it does
not cover the case with only one formal parameter in the sense that it
does not provide any semantics for the case.  We found this error
during evaluation of the Test262 tests under the extracted semantics
via \( \tool \).  The interpreter threw an error because for specific
tests no \textbf{ExpectedArgumentCount} algorithm was available.

The third error is in \textsf{Ecmarkup}~\cite{ecmarkup}, a
toolchain that specifies ECMAScript and beautifies an HTML file with
raw specification to a more readable one.  At first, we though we
found a missing case for the \textbf{IsFunctionDefinition} algorithm
of unnamed function expressions.  However, the HTML file with raw
specification contained the corresponding case.  We investigated the
issue and realized that \textsf{Ecmarkup} itself had a bug that
silently removed the {\small opt} subscript in the \( \code{collapsed} \)
syntax mode.  It was already reported in another pull request but
\( \tool \) detected it in a mechanical way.

### 2019-08-21 icse/impl.tex
Updated table
Till Sec. 6

Our goal is to extract the JavaScript syntax and semantics from the
ECMAScript 2020 specification.  It is the next ECMAScript version
that is actively updated in its GitHub repository~\cite{es2020}
to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, test262, for ECMAScript 2020.

\subsection{Excluded Language Features}
We decided not to support the following language features in ECMAScript 2020:

\paragraph{No-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
\textit{intentionally} provide slightly different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode of JavaScript to focus on the main contribution of this
paper.

\paragraph{Orthogonal Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are orthogonal
to the JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support the four libraries.

@@

\subsection{Compile Rules for ECMAScript}

\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c|r|r|r|r|r|r|r}
      \text{name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# rules}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}\\\hline
    \end{array}
  \]
\end{table}

>>>>

Our goal is to extract the JavaScript syntax and semantics from the
ECMAScript 2020 specification.  It is the next ECMAScript version
that is actively updated in its GitHub repository~\cite{es2020}
to be released in the next year.  Moreover, Ecma Technical Committee 39 (TC39)
officially provides the conformance test suite, Test262, for ECMAScript 2020.

\subsection{Excluded Language Features}\label{sec:exclusion}
We decided not to support the following language features in ECMAScript 2020:

\paragraph{Non-Strict Mode}
Since ECMAScript 5, JavaScript introduced strict mode to
\textit{intentionally} provide slightly different semantics.  It
provides more stable semantics by preventing unsafe actions or
throwing originally ignored errors.  However, the ECMAScript
specification states that ``Strict mode does not restrict or modify
any aspect of the ECMAScript semantics that must operate consistently
across multiple source text units.''  Thus, we decided to support only
strict mode of JavaScript to focus on the main contribution of this
paper.

@@

\paragraph{Inessential Built-in Objects}
JavaScript provides various standard built-in objects to support
helper functions.  However, several built-in libraries are not essential
to the core JavaScript semantics but support extra functionalities such as
\( \code{Math} \), \( \code{Date} \), \( \code{RegExp} \), and
\( \code{JSON} \).  Thus, we decided not to support such libraries
following the tradition of KJS~\cite{kjs}.

\subsection{Compile Rules for ECMAScript}
\begin{table}[t]
  \centering
  \caption{Compile rules in ECMAScript 2020}
  \label{table:rules}
\vspace*{-1em}
  \[
    \begin{array}{c?r|r|r|r|r|r|r}
      \text{Name}
      & \multicolumn{1}{c|}{\code{Stmt}}
      & \multicolumn{1}{c|}{\code{Expr}}
      & \multicolumn{1}{c|}{\code{Cond}}
      & \multicolumn{1}{c|}{\code{Value}}
      & \multicolumn{1}{c|}{\code{Ty}}
      & \multicolumn{1}{c|}{\code{Ref}}
      & \multicolumn{1}{c}{\code{SecNo}}\\\hline
      \text{\# Rules}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
      & \inred{XX}
    \end{array}
  \]
\end{table}

### 2019-08-21 icse/intro.tex
Till Sec. 6

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, test262~\cite{test262}; out of \inred{XXXXX} tests for
ECMAScript 2020 it passed \inred{XXXXX} tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  We applied
\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
passed all the tests in \inred{XX} proposals and partially passed the
tests in \inred{XX} proposals.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found \inred{X} possible specification errors in ECMAScript
2020.  They were all confirmed by TC39 and will be fixed in the next
release.
\end{itemize}

>>>>

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, Test262~\cite{test262}; out of \inred{XXXXX} tests for
ECMAScript 2020 it passed \inred{XXXXX} tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  We applied
\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
passed all the tests in \inred{XX} proposals and partially passed the
tests in \inred{XX} proposals.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found \inred{X} possible specification errors in ECMAScript
2020.  They were all confirmed by TC39 and will be fixed in the next
release.
\end{itemize}

### 2019-08-21 icse/main.tex
Changed filename framework.tex -> impl.tex
Written Section 6
Updated the number of grammars
Till Sec. 6

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

@@

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript specifications.  It also converts each
abstract algorithm written in a structured natural language into
functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications.  The compilation from algorithms to
\( \ires \) functions is defined with \textit{compile rules}.
We applied \( \tool \) to the next proposed version, ECMAScript 2020,
and the automatically extracted semantics passed all \inred{XXXXX} tests 
in test262, the official ECMAScript conformance test suite.
\inred{Moreover, \( \tool \) also successfully extracts
semantics for \inred{XX} proposed features by adding only \inred{XX}
minor compile rules.}
\end{abstract}

@@

\input{intro}
\input{overview}
\input{parser}
\input{compiler}
\input{framework}
\input{eval}
\input{related}
\input{conclusion}

>>>>

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}

@@

% thicker vertical line
\newcolumntype{?}{!{\vrule width 1pt}}

@@

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript specifications.  It also converts each
abstract algorithm written in a structured natural language into
functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications.  The compilation from algorithms to
\( \ires \) functions is defined with \textit{compile rules}.
We applied \( \tool \) to the next proposed version, ECMAScript 2020,
and the automatically extracted semantics passed all \inred{XXXXX} tests 
in Test262, the official ECMAScript conformance test suite.
\inred{Moreover, \( \tool \) also successfully extracts
semantics for \inred{XX} proposed features by adding only \inred{XX}
minor compile rules.}
\end{abstract}

@@

\input{intro}
\input{overview}
\input{parser}
\input{compiler}
\input{impl}
\input{eval}
\input{related}
\input{conclusion}
